\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
more discussions

It is difficult to avoid being disingenuous in one's solution
when the answer (or the expected answer)
to a problem is known ahead of time. Since we had access to 
``ground truth'' from the beginning, many of the de-trending/processing/fitting
choices we made were (however inadvertently) driven by the desire to
come as close as possible to the correct answer. While many of these choices
correspond to numbers we have explicitly quoted here, such as the prior
variances on our model terms, several of them are implicit decisions on
\emph{how} we performed the analysis. For instance, in an early version of 
the project we used as regressors actual \tess housekeeping variables---such as the angle 
and elevation of the Earth and the Moon relative to each of the four camera 
boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
proved to be too inflexible, judging in part from the poor fidelity of the recovered
maps. The results in this work
must therefore be taken with a grain of salt. That said, we have attempted to
offset the possibility of confirmation bias by making our model
(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
and a linear reflectance model) and thus limiting
the number of knobs we could turn. We also opted to fit for the spectral
slope of the map rather than use the power spectrum inferred from 
real imaging data. Moreover, the broad features in the strongly
regularized map (Figure~\ref{map_L2})---and in particular the monsoon clouds
over southeast Asia---are insensitive to most of our model choices.

@@

\todo{PLD, moon background, etc.}

In our analysis, we neglected the effects of limb darkening. Because of
atmospheric attenuation, features near the limb of the planet should in
reality contribute less to the flux than our model predicts. This could
bias our results particularly in cases where the planet is seen at half
phase (for instance, during days 1326 and 1341 in Figure~\ref{fig:phases}).
In the absence of limb darkening, the brightest regions on the planet are those
close to the sub-stellar point, which is on the limb. Limb darkening should
shift the regions of peak brightness closer to the center of the planet, adding
an east-west bias in the location of the features we identify.

Finally, we implicitly assumed an isotropic prior on the spherical harmonic
coefficients by imposing a power spectrum in only the degree $l$. This has the
effect of lessening the extent to which features can be confined to certain
latitudes. In particular, our prior implicitly disfavors banded cloud structure,
which one may \emph{a priori} expect on a rapidly rotating planet such as 
Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
at the equator and at mid-latitudes due to the combined effects of 
north-south circulation and deflection by the Coriolis force.

>>>>

It is difficult to avoid being disingenuous in one's solution
when the answer (or the expected answer)
to a problem is known ahead of time. Since we had access to 
``ground truth'' from the beginning, many of the de-trending/processing/fitting
choices we made were (however inadvertently) driven by the desire to
come as close as possible to the correct answer. While many of these choices
correspond to numbers we have explicitly quoted here, such as the prior
variances on our model terms, several of them are implicit decisions on
\emph{how} we performed the analysis. For instance, in an early version of 
the project we used as regressors actual \tess housekeeping variables---such as the angle 
and elevation of the Earth and the Moon relative to each of the four camera 
boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
proved to be too inflexible, judging in part from the poor fidelity of the recovered
maps. The results in this work
must therefore be taken with a grain of salt. That said, we have attempted to
offset the possibility of confirmation bias by making our model
(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
and a linear reflectance model) and thus limiting
the number of knobs we could turn. We also opted to fit for the spectral
slope of the map rather than use the power spectrum inferred from 
real imaging data. Moreover, the broad features in the strongly
regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
over southeast Asia---are insensitive to most of our model choices.

One of the largest sources of bias is the fact that we assumed our
systematics model is strictly multiplicative. Although we subtracted
an estimate of the baseline non-Sol d background flux from each target
(measured from the mid-sector portions of the light curve where the
planet was below the edge of the sunshade), we implicitly assumed
that this constant baseline was the \emph{only} source of additive
noise. We know this to be strictly untrue, as Sol d is known to
have a companion (Sol d I), a moon about one-third the diameter of 
Sol d, whose reflected light should cause periodic modulations
in the background flux of \tess pixels. Because of its small size and
very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
is likely to contaminate our signal at certain points in the orbit
where \tess is closer to Sol d I than to Sol d. While this will
likely bias the \starry model at those times, the effect is particularly
concerning because of its impact on the PLD basis. While PLD can be an
extremely powerful de-trending technique, it is notorious for
grossly overfitting signals in the presence of uncorrected background
modulations \citep{Luger2016}. This happens because PLD strictly
assumes the noise is multiplicative, which is not the case for 
signals with varying (additive) background levels. In principle, one
could model the reflectance variability of Sol d I in the same way as
we did here, but since the optics are not well understood, this 
may be difficult in practice.

In our analysis, we also neglected the effects of limb darkening. Because of
atmospheric attenuation, features near the limb of the planet should in
reality contribute less to the flux than our model predicts. This could
bias our results particularly in cases where the planet is seen at half
phase (for instance, during days 1326 and 1341 in Figure~\ref{fig:phases}).
In the absence of limb darkening, the brightest regions on the planet are those
close to the sub-stellar point, which is on the limb. Limb darkening should
shift the regions of peak brightness closer to the center of the planet, adding
an east-west bias in the location of the features we identify.

Moreover, we implicitly assumed an isotropic prior on the spherical harmonic
coefficients by imposing a power spectrum in only the degree $l$. This has the
effect of lessening the extent to which features can be confined to certain
latitudes. In particular, our prior implicitly disfavors banded cloud structure,
which one may \emph{a priori} expect on a rapidly rotating planet such as 
Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
at the equator and at mid-latitudes due to the combined effects of 
north-south circulation and deflection by the Coriolis force.

Finally, and perhaps more importantly, our model assumed a \emph{static}
map for the surface of Sol d. We also know this to be incorrect, since
clouds form and move on timescales of hours to days. We discuss this in
detail next.

@@
